Constant-round Blind Classical Verification of Quantum Sampling

### 2020-10-03 preliminaries.tex
Fix typo

We define the sampling version of $\BQP$ based on \cite{aaronson_2013, aaronson_arkhipov_2011}.
The definition of $\SampBQP$ allows inverse-polynomial error in order to capture some characteristics of optics-based quantum computing implementations.

>>>>

We define $\SampBQP$ based on \cite{aaronson_2013, aaronson_arkhipov_2011}.
\Ethan{Tried to explain better}
This complexity class is meant to model feasible quantum computations.
It is worth noting that quantum states live in a Hilbert space which is continuous,
so it is likely that any physical implementation of quantum computing would naturally involve some sort of errors.
\cite{aaronson_arkhipov_2011} gives an argument from the physical implementation perspective that this error should be inverse polynomial.
